\documentclass{article}
\usepackage[margin=1.25in]{geometry}
\usepackage{amsmath, amsfonts, enumitem}

\newcommand{\F}{\mathbb{F}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\vv}{\mathrm{v}}
\newcommand{\ww}{\mathrm{w}}
\newcommand{\zero}{\mathrm{0}}

\begin{document}
\begin{enumerate}[label=\textbf{7.\arabic*.}]
    \item $X, Y$ are subspaces of a vector space $V$, that is they are closed
    under vector addition and scalar multiplication. It follows $X\cap Y$ is
    closed under vector addition and scalar for it only contains vectors in both
    $X$ and $Y$.

    \item Let $\vv_{x, 1},\ldots,\vv_{x, n}$ be a basis in $X$ and
    $\vv_{y, 1},\ldots,\vv_{y,m}$ be a basis in $Y$. Then, linear combination
    of the two bases generates $X+Y$ by definition. Any vectors $\vv_1, \vv_2$
    in $X+Y$ are linear combination of the two bases, and closed under
    vector addition. The same holds for scalar multiplication which merely
    scales the vector, multiplies all co-efficients by a scalar.

    Note: it's not claimed linear combination of two bases will admit
    unique representation for a vector in $X+Y$.

    \item Assume $\vv+\mathrm{x}$ is in some subpsace $V_0$ for any $\mathrm{x}$
    in $V_0$ and $\vv$ being not. For $\mathrm{x} = \zero$, $\vv$ is in
    $V_0$, and we contradict our assumption.
    
    \item Suppose $\vv$ is a vector in subspace $X\cup Y$. Note $X$ is a subset
    of $X\cup Y$, for $\mathrm{x}$ in $X$ and $\vv$ not in $X$,
    $\vv + \mathrm{x}$ is in $Y$. With $Y$ being a subpsace, it must contain
    $\vv$ and its additive inverse, and $\vv + \mathrm{x} - \vv = \mathrm{x}$
    is in $Y$ by closure. Or, $X$ is a subset of $Y$.

    \item Define $e_{i, j}$ as matrix with all entries 0 but $(i, j)$th
    one being 1. The smallest subpsace for upper triangular matrices of
    $4\times 4$ would be linear span of vectors $e_{i, j}$ with
    $0< i\leq j\leq 4$ as it only contains upper-triangular matrices and zero.
\end{enumerate}
\end{document}